Automatic Parallelization and Transparent Fault Tolerance\\ (\emph{New project} paper)

### 2016-04-15 pubs/tfp16/paper.tex
CodeGen.hs adds extra arg to stgApply, fix strictness in stgapply.c

An almost unbounded amount of interesting development suggests itself; one
such path would lead to the recreation of GHC.  However, given the minuscule
budget (and therefore the employment of student interns) we must maintain
sharp focus on the main goals: implementing and evaluating mechanisms for
automatic parallelism and fault tolerance.  At the time of writing we have a
fully functioning serial implementation including
\begin{itemize}
\item STG parser \emph{(by student)},
\item mini-Haskell parser, mini-Haskell to STG transformer \emph{(by student)},
\item type inferencer,
\item various analysis and transformation passes \emph{(some by students)},
\item code generator \emph{(some student contribution)},
\item runtime system including a garbage collector,
\item continuous integration and testing system,
\item extensive test suite \emph{(mostly by students)}.
\end{itemize}

@@

Various papers describing some of the inner workings of GHC at various points
in its evolution have greatly informed our approach and these have all been
previously cited.

@@

Recently, Robert Stewart extended Haskell Distributed Parallel Haskell
(HdpH)~\cite{hdph} to be fault resilient at an impressive scale---1400 cores
on a distributed memory system.  Here the key recovery strategy is task
replication~\cite{Stewart:2013}.

>>>>

An almost unbounded amount of interesting development suggests itself; one
such path would lead to the recreation of GHC.  However, given the minuscule
budget (and therefore the employment of student interns) we must maintain
sharp focus on the main goals: implementing and evaluating mechanisms for
automatic parallelism and fault tolerance.  At the time of writing we have a
fully functioning serial implementation including
\begin{itemize}
\item STG parser \emph{(by student)},
\item mini-Haskell parser, mini-Haskell to STG transformer \emph{(by student)},
\item type inferencer,
\item various analysis and transformation passes \emph{(some by students)},
\item code generator \emph{(some student contribution)},
\item runtime system including a garbage collector,
\item continuous integration and testing system,
\item extensive test suite \emph{(mostly by students\footnote{Many are
    students' solutions to exercises in learning algorithms and data
    structures.})}.
\end{itemize}

@@

Previously cited papers describing some of the inner workings of GHC at
various points in its evolution have greatly informed our approach.

@@

More recently, Robert Stewart extended Haskell Distributed Parallel Haskell
(HdpH)~\cite{hdph} to be fault resilient at an impressive scale---1400 cores
on a distributed memory system.  Here the key recovery strategy is task
replication~\cite{Stewart:2013}.
